### 2024-05-24 getting-started.qmd
20240524 - add data files

@@

>>>>

### Game Schedules {#sec-downloadSchedules}

nfl_schedules <- progressr::with_progress(
  nflreadr::load_schedules(seasons = TRUE))
```

save(
  nfl_schedules,
  file = here("data", "nfl_schedules.RData")
)
```

load(file = here("data", "nfl_schedules.RData"))
```

### Draft Picks {#sec-draftPicks}

nfl_draftPicks <- progressr::with_progress(
  nflreadr::load_draft_picks(seasons = TRUE))
```

save(
  nfl_draftPicks,
  file = here("data", "nfl_draftPicks.RData")
)
```

load(file = here("data", "nfl_draftPicks.RData"))
```

@@

### Injuries {#sec-injuries}

nfl_injuries <- progressr::with_progress(
  nflreadr::load_injuries(seasons = TRUE))
```

save(
  nfl_injuries,
  file = here("data", "nfl_injuries.RData")
)
```

load(file = here("data", "nfl_injuries.RData"))
```

### Snap Counts {#sec-snapCounts}

nfl_snapCounts <- progressr::with_progress(
  nflreadr::load_snap_counts(seasons = TRUE))
```

save(
  nfl_snapCounts,
  file = here("data", "nfl_snapCounts.RData")
)
```

load(file = here("data", "nfl_snapCounts.RData"))
```

### ESPN QBR {#sec-espnQBR}

nfl_espnQBR_seasonal <- progressr::with_progress(
  nflreadr::load_espn_qbr(
    seasons = TRUE,
    summary_type = c("season")))

nfl_espnQBR_weekly <- progressr::with_progress(
  nflreadr::load_espn_qbr(
    seasons = TRUE,
    summary_type = c("weekly")))

nfl_espnQBR_weekly$game_week <- as.character(nfl_espnQBR_weekly$game_week)

nfl_espnQBR <- bind_rows(
  nfl_espnQBR_seasonal,
  nfl_espnQBR_weekly
)
```

save(
  nfl_espnQBR,
  file = here("data", "nfl_espnQBR.RData")
)
```

load(file = here("data", "nfl_espnQBR.RData"))
```

### Advanced Stats from PFR {#sec-advancedStatsPFR}

nfl_advancedStatsPFR_pass_seasonal <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("pass"),
    summary_level = c("season")))

nfl_advancedStatsPFR_pass_weekly <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("pass"),
    summary_level = c("week")))

nfl_advancedStatsPFR_rush_seasonal <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("rush"),
    summary_level = c("season")))

nfl_advancedStatsPFR_rush_weekly <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("rush"),
    summary_level = c("week")))

nfl_advancedStatsPFR_rec_seasonal <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("rec"),
    summary_level = c("season")))

nfl_advancedStatsPFR_rec_weekly <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("rec"),
    summary_level = c("week")))

nfl_advancedStatsPFR_def_seasonal <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("def"),
    summary_level = c("season")))

nfl_advancedStatsPFR_def_weekly <- progressr::with_progress(
  nflreadr::load_pfr_advstats(
    seasons = TRUE,
    stat_type = c("def"),
    summary_level = c("week")))

nfl_advancedStatsPFR <- bind_rows(
  nfl_advancedStatsPFR_pass_seasonal,
  nfl_advancedStatsPFR_pass_weekly,
  nfl_advancedStatsPFR_rush_seasonal,
  nfl_advancedStatsPFR_rush_weekly,
  nfl_advancedStatsPFR_rec_seasonal,
  nfl_advancedStatsPFR_rec_weekly,
  nfl_advancedStatsPFR_def_seasonal,
  nfl_advancedStatsPFR_def_weekly,
)
```

save(
  nfl_advancedStatsPFR,
  file = here("data", "nfl_advancedStatsPFR.RData")
)
```

load(file = here("data", "nfl_advancedStatsPFR.RData"))
```

### Player Contracts {#sec-playerContracts}

nfl_playerContracts <- progressr::with_progress(
  nflreadr::load_contracts())
```

save(
  nfl_playerContracts,
  file = here("data", "nfl_playerContracts.RData")
)
```

load(file = here("data", "nfl_playerContracts.RData"))
```

### FTN Charting Data {#sec-ftnCharting}

nfl_ftnCharting <- progressr::with_progress(
  nflreadr::load_ftn_charting(seasons = TRUE))
```

save(
  nfl_ftnCharting,
  file = here("data", "nfl_ftnCharting.RData")
)
```

load(file = here("data", "nfl_ftnCharting.RData"))
```

### Fantasy Player IDs {#sec-fantasyPlayerIDs}

nfl_playerIDs <- progressr::with_progress(
  nflreadr::load_ff_playerids())
```

save(
  nfl_playerIDs,
  file = here("data", "nfl_playerIDs.RData")
)
```

load(file = here("data", "nfl_playerIDs.RData"))
```

### FantasyPros Rankings {#sec-fantasyProsRankings}

#nfl_rankings <- progressr::with_progress( # currently throws error
#  nflreadr::load_ff_rankings(type = "all"))

nfl_rankings_draft <- progressr::with_progress(
  nflreadr::load_ff_rankings(type = "draft"))

nfl_rankings_weekly <- progressr::with_progress(
  nflreadr::load_ff_rankings(type = "week"))

nfl_rankings <- bind_rows(
  nfl_rankings_draft,
  nfl_rankings_weekly
)
```

save(
  nfl_rankings,
  file = here("data", "nfl_rankings.RData")
)
```

load(file = here("data", "nfl_rankings.RData"))
```

### Expected Fantasy Points {#sec-expectedFantasyPoints}

nfl_expectedFantasyPoints_weekly <- progressr::with_progress(
  nflreadr::load_ff_opportunity(
    seasons = TRUE,
    stat_type = "weekly",
    model_version = "latest"
  ))

nfl_expectedFantasyPoints_pass <- progressr::with_progress(
  nflreadr::load_ff_opportunity(
    seasons = TRUE,
    stat_type = "pbp_pass",
    model_version = "latest"
  ))

nfl_expectedFantasyPoints_rush <- progressr::with_progress(
  nflreadr::load_ff_opportunity(
    seasons = TRUE,
    stat_type = "pbp_rush",
    model_version = "latest"
  ))

nfl_expectedFantasyPoints_weekly$season <- as.integer(nfl_expectedFantasyPoints_weekly$season)

nfl_expectedFantasyPoints_offense <- bind_rows(
  nfl_expectedFantasyPoints_pass,
  nfl_expectedFantasyPoints_rush
)
```

save(
  nfl_expectedFantasyPoints_weekly,
  file = here("data", "nfl_expectedFantasyPoints_weekly.RData")
)

save(
  nfl_expectedFantasyPoints_offense,
  file = here("data", "nfl_expectedFantasyPoints_offense.RData")
)
```

load(file = here("data", "nfl_expectedFantasyPoints_weekly.RData"))

load(file = here("data", "nfl_expectedFantasyPoints_offense.RData"))
```
